---
title: "Biological Stressor Identification Process"
author: "Christopher Main"
date: "June 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
Abbreviation | Full Name
----- | -------
CM | Channel Modification
IH | Instream Habitat
P | Pools
BSL | Bank Stability (Left)
BSR | Bank Stability (Right)
BVL | Bank Vegetative (Left)
BVR | Bank Vegetative (Right)
S | Shading
RZL | Riparian Zone Width (Left)
RZR | Riparian Zone Width (Right)
Alkalinity | Alkalinity (Titrimetric, pH 4.5)
NH3 | Ammonia as N, Total
CBOD20 | BOD, 20-Day, N-Inhib (CBOD20)
CBOD5 | BOD, 5-Day, N-Inhib (CBOD5)
DOC | Carbon, Organic - Dissolved (DOC)
TOC | Carbon, Organic - Total (TOC)
Chloride | Chloride, Total
Chla | Chlorophyll-a
SpCond | Conductance, Specific - Field
Flow | Flow, Cubic Feet Per Second
Hardness | Hardness as CaCO3
NOx | Nitrate/Nitrite as N, Total
TN | Nitrogen, Total, Alkaline Persulfate
OP | Orthophosphorus, Soluable
DO | Oxygen, Dissolved - Membrane Electrode
pH | pH, Field
TP | Phosphorus, Total, Alkaline Persulfate
TSS | Residue, Nonfilterable (TSS)
Salinity | Salinity
ATemp | Temperature, Air
Temp | Temperature, Water
Turbidity | Turbidity (Nephelometric)



## Data cleanup and export

Data from 2005 to Present is used for determining stressors.
```{r datacleanup}
# Clean up of Chemical tests
chem = read.csv('csv/Chem_2005-Present.csv')
chem = chem %>% separate(SampleNumber, c('OrderID', 'Sample'), '-')
chem.spread = chem %>% spread(Test, Results) %>% rename(Collection.Date = CollectDate)

# Clean up of Habitat numbers
cp.hab = read.csv('csv/CP_Hab_assess_1999-Present.csv')
cp.hab = cp.hab %>% separate(Sample.., c('OrderID', 'Sample'), '-') %>% rename(Site = Site.ID)
cp.hab$Site = as.factor(cp.hab$Site)

# Clean up of Bug numbers
cp.bugs = read.csv('csv/CP_Bio_assess_1999-Present.csv')
cp.bugs = cp.bugs %>% separate(Sample.., c('OrderID', 'Sample'), '-') %>% rename(Site = Site.ID)
cp.bugs$Site = as.factor(cp.bugs$Site)

# Join everything with bug data
cp = inner_join(cp.hab, cp.bugs, by = c('OrderID', 'Site')) %>% inner_join(chem.spread) %>% select(-Sample.y, -Collection.Date.y, -Sample.x, -Comment, -CustomerSampleNumber, -Collection.Date.x) %>% distinct(Site, OrderID, .keep_all = TRUE)

# Combine Good and Excellent Conditions
cp = cp %>% mutate(Biotic.Classification = replace(Biotic.Classification, which(Biotic.Classification == 'Good condition'), 'Good Condition'), Biotic.Classification = replace(Biotic.Classification, which(Biotic.Classification == 'Moderately degraded'), 'Moderately Degraded'), Biotic.Classification = replace(Biotic.Classification, which(Biotic.Classification == 'Severely degraded'), 'Severely Degraded'), Biotic.Classification = replace(Biotic.Classification, which(Biotic.Classification == 'Excellent'), 'Good Condition'))

write.csv(cp, 'csv/Coastal_plain.csv', row.names = FALSE)
```

## Bootstrap analysis
```{r bootstrap}
library(slipper)
cp = read.csv('csv/Coastal_plain.csv')
cp = cp %>% 
  select(OrderID, Site, Watershed, Site.Location, Collection.Date, Habitat.Index = Habitat.Index.., Habitat.Classification, Biotic.Index = Biotic.Index...., Biotic.Classification, CM, IH, P, BSL, BSR, BVL, BVR, S, RZL, RZR, Alkalinity = Alkalinity..Titrimetric..pH.4.5., NH3 = Ammonia.as.N..Total, CBOD20 = BOD..20.Day..N.Inhib..CBOD20., CBOD5 = BOD..5.Day..N.Inhib..CBOD5., DOC = Carbon..Organic...Dissolved..DOC., TOC = Carbon..Organic...Total..TOC., Chloride = Chloride..Total, Chla = Chlorophyll.a, SpCond = Conductance..Specific...Field, Hardness = Hardness.as.CaCO3, NOx = Nitrate.Nitrite.as.N..Total, TN = Nitrogen..Total..Alkaline.Persulfate, OP = Orthophosphorus..Soluable, DO = Oxygen..Dissolved...Membrane.Electrode, OSat = Oxygen..Dissolved...Saturation, pH = pH..Field, TP = Phosphorus..Total..Alkaline.Persulfate, TSS = Residue..Nonfilterable..TSS., Salinity, ATemp = Temperature..Air, Temp = Temperature..Water, Turbidity = Turbidity..Nephelometric., Flow = Flow..Cubic.Feet.Per.Second)

cm.boot = cp %>%
  group_by(Biotic.Classification) %>% 
  do(slipper(mean(CM), B = 10000, df = .)) %>% 
  summarize('Lower Int' = quantile(value, 0.2), mean = mean(value), 'Upper Int' = quantile(value, 0.8))
ih.boot = cp %>%
  group_by(Biotic.Classification) %>% 
  do(slipper(mean(IH), B = 10000, df = .)) %>% 
  summarize('Lower Int' = quantile(value, 0.2), mean = mean(value), 'Upper Int' = quantile(value, 0.8))
p.boot = cp %>%
  group_by(Biotic.Classification) %>% 
  do(slipper(mean(P), B = 10000, df = .)) %>% 
  summarize('Lower Int' = quantile(value, 0.2), mean = mean(value), 'Upper Int' = quantile(value, 0.8))

knitr::kable(x = cm.boot,
             digits = 1,
             caption = 'Channel Modification',
             col.names = c('Biotic Classification',
             'Lower 20% Limit',
             'Mean',
             'Upper 20% Limit'),
             align = c('l','c','c','c'))
```